---
title: "README"
author: "Luke Higgins"
date: "`r Sys.Date()`"
output:
  github_document:
    html_preview: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ReMEA
## Response Marker Enrichment Analysis
`ReMEA` is an enrichment analysis method, whereby protein perturbation response
signatures are used to score perturbations according to the inferred sensitivity
profile.

## Installation
### R console
#### One-liner
Run: `devtools::install_github("CutillasLab/ReMEA")`

- You may first need to install `devtools`: `install.packages("devtools")`

### Manual
1. Download the Package Archive File (ReMEAx.x.x.tar.gz) of the latest release.
    - Not the Source code
2. Run: devtools::install_local(path = "C:/path/to/ReMEAx.x.x.tar.gz")
    - Replace the string argument to path with the actual location
    - You may first need to install `devtools`: `install.packages("devtools")`

## Usage
For a complete analysis of your data, the `ReMEA::complete_ReMEA_analysis` function
runs the analysis for all perturbation modalities and signatures. Default settings
apply the analysis using the "CellLines" signatures. This returns a list of all the 
resulting scores. This includes the individual db scores and main ReMEA score (av.effect).
```{r, eval=FALSE}
results <- ReMEA::complete_ReMEA_analysis(protein_data = proteomics_data)
```
We to analyse data using signatures derived from the beat AML data, enter select 
the "BeatAML" signatures in the function. In addition, the haem tumour type must 
be specified:
```{r, eval=FALSE}
results <- ReMEA::complete_ReMEA_analysis(protein_data = proteomics_data,
                                          signature_version = "BeatAML",
                                          tumour_type = c("haem"))
```
The core component of ReMEA is the `ReMEA::response_marker_enrichment_analysis` 
function. If you wish use use specific signature sets, these can be specified here:
```{r, eval=FALSE}
results <- ReMEA::response_marker_enrichment_analysis(protein_data = proteomics_data,
                                                      marker_type = "DRUG",
                                                      tumour_type = "pan",
                                                      signature_version = "CellLines")
```
If you wish to use your own signatures, this can be achieved using the base 
`ReMEA::signature_enrichment` function.

## Interpretation of results
The primary score for interpretation is the av.effect score, this is the principal
ReMEA score which incorporates the output from the different signature sets (constructed
from the different cell line proteomics datasets).

A positive ReMEA score (av.effect) is interpreted as an increase in sensitivity
to that perturbation. A negative score suggests resistance to that perturbation.
The magnitude of scores can differ between datasets (similar to other enrichment
methods). Accompanying p-values and overall ranking of scores should be used to
interpret the returned scores.

## Interpretation of results
For reference, an explanation 
of the fields from the output can be reviewd using the `ReMEA::output_description` 
function.
```{r}
ReMEA::output_description(
  combined_scores = TRUE,
  individual_scores = FALSE
)
```
To further investigate a particular ReMEA score, the individual dataset signature
metrics can be reviewed. See below for a description of the data fields.
```{r}
ReMEA::output_description(
  combined_scores = FALSE,
  individual_scores = TRUE
)
```
