---
title: "Quick start"
author: "Luke Higgins"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Usage
For a complete analysis of your data, the `ReMEA::complete_ReMEA_analysis` function
runs the analysis for all perturbation modalities and signatures. Default settings
apply the analysis using the "CellLines" signatures. This returns a list of all the 
resulting scores. This includes the individual db scores and main ReMEA score (av.effect).

These fall under the "_combined" and "_individual_dbs" slots. The combined set 
represent the main ReMEA output, with the composite ReMEA score across all signatures.
The "individual_dbs" score sets represents the scores from individual signature sets.

Ensure your data has proteins annotated with their Uniprot Entry Name. This column
can be specified with the `protein_id_col` argument. If not specified, the first 
column with be used to the protein ID. Similarly, the numeric column to be analysed
(e.g. fold change) can be specified with the `analysis_col` argument. If not
specified, the second column will be used for input.
```{r, eval=FALSE}
results <- ReMEA::complete_ReMEA_analysis(protein_data = proteomics_data)
```
The core component of ReMEA is the `ReMEA::response_marker_enrichment_analysis` 
function. If you wish use use specific signature sets, these can be specified here:
```{r, eval=FALSE}
results <- ReMEA::response_marker_enrichment_analysis(protein_data = proteomics_data,
                                                      marker_type = "DRUG",
                                                      tumour_type = "pan",
                                                      signature_version = "CellLines")
```
Tumour type and signature version arguments are to specify particular signatures.
All signatures from cell lines are constructed using a `pan` cancer context.

If you wish to use your own signatures, this can be achieved using the base 
`ReMEA::signature_enrichment` function.

## Interpretation of results
The primary score for interpretation is the av.effect score, this is the principal
ReMEA score which incorporates the output from the different signature sets (constructed
from the different cell line proteomics datasets).

A positive ReMEA score (av.effect) is interpreted as an increase in sensitivity
to that perturbation. A negative score suggests resistance to that perturbation.
The magnitude of scores can differ between datasets (similar to other enrichment
methods). Accompanying p-values and overall ranking of scores should be used to
aid the interpretation of the returned scores.

## Description of the output
For reference, an explanation of the fields from the output can be reviewed
using the `ReMEA::output_description` function. Note, the drug perturbations are 
those from the GDSC2 dataset, and are labelled as they are from direct download 
from the GDSC2 resource.
```{r}
ReMEA::output_description(
  combined_scores = TRUE,
  individual_scores = FALSE
)
```
To further investigate a particular ReMEA score, the individual dataset signature
metrics can be reviewed. See below for a description of the data fields.
```{r}
ReMEA::output_description(
  combined_scores = FALSE,
  individual_scores = TRUE
)
```
