---
title: "Quick start"
author: "Luke Higgins"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Usage
For a complete analysis of your data, the `ReMEA::complete_ReMEA_analysis` function
runs ReMEA  for all perturbation modalities and cell line signatures(`signature_version = "CellLines"`). 
This returns a list of all the resulting score tables, including the individual 
signature scores and main ReMEA score (av.effect).

Output tables fall under the "_combined" and "_individual_dbs" slots. The combined set 
represent the main ReMEA output, that is, the composite ReMEA score across all signatures.
The "individual_dbs" score sets represents the scores from individual signature sets
(derived from specific datasets).

For the analysis, ensure your proteomics data is a `data.table` or `data.frame` 
(which will be converted internally into a `data.table`). Proteins must annotated with 
their Uniprot Entry Name. This column name can be specified with the `protein_id_col` 
argument. If not specified, the first column with be used for the protein ID. 
Similarly, the numeric column to be analysed (e.g. fold change) can be specified 
with the `analysis_col` argument. If not specified, the second column will be used for input.

For a complete analysis using all cell line signatures, run:
```{r, eval=FALSE}
results <- ReMEA::complete_ReMEA_analysis(protein_data = proteomics_data)
```
If you wish use use specific perturbation types, the `ReMEA::get_ReMEA_scores` function
can be used as a convenient way to get specific perturbation modality scores. For example:
```{r, eval=FALSE}
results <- ReMEA::get_ReMEA_scores(protein_data = proteomics_data,
                                   marker_type = "RNAi",
                                   tumour_type = "pan",
                                   signature_version = "CellLines")
```
Tumour type and signature version arguments are used to specify particular signatures.
All signatures from cell lines are constructed using a `pan` cancer context, and this
forms the bulk of the signatures available currently.

## Interpretation of results
The primary score for interpretation is the av.effect score. This is the principal
ReMEA score which incorporates the output from the different signature sets (constructed
from the different cell line proteomics datasets).

A positive ReMEA score (av.effect) is interpreted as an increase in markers of sensitivity
to that perturbation. A negative score suggests enrichment of resistance markers to that perturbation.
The magnitude of scores can differ between datasets (similar to other enrichment
methods). Accompanying p-values and overall ranking of scores should be used to
aid the interpretation of the returned results.

## Description of the output
For reference, an explanation of the fields from the output can be reviewed
using the `ReMEA::output_description` function. Note, the drug perturbations are 
those from the GDSC2 dataset, and are labelled as they are from the direct download 
from the GDSC2 resource.
```{r}
ReMEA::output_description(
  combined_scores = TRUE,
  individual_scores = FALSE
)
```
To further investigate a particular ReMEA score, the individual dataset signature
metrics can be reviewed. See below for a description of the data fields.
```{r}
ReMEA::output_description(
  combined_scores = FALSE,
  individual_scores = TRUE
)
```
